Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-15 paper/ijcai/paper.tex
another update

        \lang{}            & 0.77\% & 30.28\%\\
        \cmath{}           &  & \\
        \closure{}          &  & \\
		\chart{}			& 59.30\% & 53.64\% \\
        \jtime{}            & 17.27\% & 32.92\%\\
        \mockito{}          & 16.99\% & 21.67\%\\

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
		\midrule
		$<0$  & 20.00\% & 17.42\% \\
		$=0$  & 47.10\% & 37.42\% \\
		$>0$  & 32.90\% & 45.16\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 387.46     & 576.74   & 522.35   \\ \midrule
Median & 44.50      & 48.25               & 46.00                \\ \midrule
Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
  \label{table:st}
\end{table*}

>>>>

        \lang{}            & 1.42\% & 30.47\%\\
        \cmath{}           & 9.88\% & 11.43\%\\
        \closure{}          &  & \\
		\chart{}			& 59.30\% & 53.64\% \\
        \jtime{}            & 17.27\% & 32.02\%\\
        \mockito{}          & 16.54\% & 21.67\%\\

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
		\midrule
		$<0$  & 19.53\% & 16.02\% \\
		$=0$  & 46.88\% & 41.80\% \\
		$>0$  & 33.59\% & 42.19\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
  \label{table:st}
\end{table*}
